\vspace{0.1cm}
\sectionTitle{Publications}{\faBook}

\vspace{0.2cm}
\begin{enumerate}
	\item \textbf{Saleh Mozaffari}, Pascal Klein, Mohammad Al-Naser, Stefan Küchemann,
	Jochen Kuhn1, Thomas Widmann, and Andreas Dengel.  Quantifying Gaze-based Strategic Patterns in Physics Vector Field Divergence. In Agents and Artificial Intelligence. Lecture Lecture Notes in Artificial Intelligence book sub series (LNAI). Springer International Publishing, 2021. (Under publication)
	\item Pascal Klein, Jouni Viiri, \textbf{Saleh Mozaffari}, Andreas Dengel, and Jochen Kuhn. Instruction-based clinical eye-tracking study on the visual interpretation of divergence: How do students look at vector field plots? In Physical Review Physics Education Research 14 (1), 010116, American Physical Society,2018.

	\item \textbf{Saleh Mozaffari}, Pascal Klein, Mohammad Al-Naser, Stefan Küchemann, Jochen Kuhn1, Thomas Widmann, and Andreas Dengel. Classification of Visual Strategies in Physics Vector Field Problem-solving. In Proceedings of the 12th International Conference on Agents and Artificial Intelligence - Volume 2: ICAART, 2020.
	\item \textbf{Saleh Mozaffari}, Pascal Klein, Jouni Viiri, Sheraz Ahmed, Jochen Kuhn, and Andreas Dengel.  Evaluating similarity measures for gaze patterns in the context of representational competence in physics education. Proceedings of the 2018 ACM Symposium on Eye-tracking Research and Applications (ETRA), 2018.
	\item \textbf{Saleh Mozaffari}, Federico Raue, Saeid Dashti Hassanzadeh, Stefan Agne, Syed Saqib Bukhari, Andreas Dengel. Reading type classification based on generative models and bidirectional long short-term memory. International Conference on Intelligent User Interface (IUI), UISTDA Workshop, Japan, Tokyo, 2018.
	\item Marc Beck, \textbf{Saleh Mozaffari}, Syed Saqib Bukhari, Andreas Dengel. Landscape or Portrait? The Impact of Page Orientation on the Understandability of Scientific Posters. 14th IAPR International Conference on Document Analysis and Recognition (ICDAR), 2017.
	\item \textbf{Saleh Mozafari}, Mohammad Al-Naser, Syed Saqib Bukhari, Damian Borth, Shanley EM Alleny, Andreas Dengel.  An eye movement study on scientific papers using wearable eye-tracking technology. 2016 Ninth International Conference on Mobile Computing and Ubiquitous Networking (ICMU), Kaiserslautern, Germany, 2016.
	\item \textbf{Saleh Mozafari}, Pascal Klein, Syed Saqib Bukhari, Jochen Kuhn, Andreas Dengel. Entropy-based transition analysis of eye movement on physics representational competence. Proceedings of the 2016 ACM International Joint Conference on Pervasive and Ubiquitous Computing, WAHM, 2016
	\item \textbf{Saleh Mozafari}, Pascal Klein, Syed Saqib Bukhari, Jochen Kuhn, Andreas Dengel. A study on representational competence in physics using mobile eye-tracking systems. Proceedings of the 18th International Conference on Human-Computer Interaction with Mobile Devices and Services, 2016.
	\item \textbf{Saleh Mozafari}, Syed Saqib Bukhari, Andreas Dengel. Analysis of Text Layout Quality Using Wearable Eye-trackers. IEEE  International Conference on Multimedia and Expo Workshops (ICMEW), 2015.
	\item Mohammad Al-Naser, Peter Lanzer, Andreas Dengel, Syed Saqib Bukhari, \textbf{Saleh Mozafari}.  Knowledge transfer from experts to novices in minimally invasive catheter-mediated (MIC) interventions, eye-tracking study. Proceedings of the 18th International Conference on Human-Computer Interaction with Mobile Devices and Services, 2016.
	\item Mohammad Al-Naser, \textbf{Saleh Mozafari}, Syed Saqib Bukhari, Damian Borth, Andreas Dengel. What Makes a Beautiful Landscape Beautiful: Adjective Noun Pairs Attention by Eye-Tracking and Gaze Analysis. Proceedings of the 1st International Workshop on Affect and Sentiment in Multimedia, 2015.
	\item Marco Stricker, Syed Saqib Bukhari, Mohammad Al Naser, \textbf{Saleh Mozafari}, Damian Borth, Andreas Dengel.  Which Saliency Detection Method is the Best to Estimate the Human Attention for Adjective Noun Concepts? International Conference on Agents and Artificial Intelligence (ICAART), 2017.
	\item M Mohammadi, \textbf{Saleh Mozaffari}, Aradhya VN Manjunath, G Hemantha Kumar. An Improved Handwritten Text Line Segmentation Technique. Advances in Computing and Communications. Pages 289-296, 2011.
\end{enumerate}

