% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Work Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
  {Present}{Expert Data Scientist | Machine Learning Engineer}{WidasConcepts GmbH}{Wimsheim, Germany}
  {Sep 2018} {
  \vspace{0.1cm}
  \textbf{Project}: Cidaas-ID-Validator
    \begin{itemize}
    \item Directed the development and deployment of scalable microservices to operationalize machine learning models, enhancing system efficiency and responsiveness.
	\item Innovated an OCR (Optical Character Recognition) model tailored for high-precision information extraction from various identity documents, significantly improving the accuracy of data retrieval processes.
	\item Engineered a sophisticated security check framework for identity verification, integrating Computer Vision and Probabilistic Graphical Models to detect fraudulent documents effectively.
	\item Pioneered the design and development of a Human-Computer Interaction (HCI) application leveraging eye-tracking methodologies (ninoxipy) for real-time liveness detection, setting new standards in identity verification technology.
	\item Played a pivotal role in the conceptualization and implementation of an MLOps framework, facilitating seamless model integration, monitoring, and management, thereby ensuring continuous improvement and operational excellence of deployed machine learning solutions.
    \end{itemize}
  }
    {Docker, Kubernetes, GitLab, DC/OS, Python, C++, R,  OpenCV, dlib, Ray, tesseract, ocrupy, Flask, Jupyter-notebook, numpy, scipy, pandas, matplotlib, seaborn, PyTorch, Pyro, Tensorflow, keras, scikit-learn, scikit-image, scikt-fuzzy}
  \emptySeparator
  \experience
	{Present}{Lead Data Scientist | Machine Learning Engineer}{WidasConcepts GmbH}{Wimsheim, Germany}
	{2020} {
	\vspace{0.1cm}
	\textbf{Project}: Cidaas- FDS (Fraud Detection System)
	\begin{itemize}
		\item Architected an ML-based cybersecurity solution, focusing on the integration of advanced fraud detection mechanisms within the system's core to bolster security measures.
		\item Engineered RESTful APIs to seamlessly serve fraud detection models, enabling real-time fraud analysis and immediate response to security threats.
		\item Instrumental in the development and maintenance of a CI/CD pipeline, ensuring the agile deployment and rigorous testing of models, which contributed to a streamlined development process.
		\item Innovated a Smart Multi-Factor Authentication (MFA) system utilizing a Fuzzy Inference System (FIS), which enhanced user verification processes by adapting to varying risk levels.
		\item Conducted Causal Inference analysis to identify the root causes of fraudulent activities, enabling the implementation of targeted preventive measures.
		\item Achieved a breakthrough in fraud detection accuracy, reaching a very high accuracy rate of 97\%, significantly reducing the risk and impact of fraudulent activities on the platform.
	\end{itemize}
}
{MLFlow, scikit-learn, scikit-image, scikt-fuzzy, CausalInference, Docker, Kubernetes, GitLab, Python, R,  FastAPI, Jupyter-notebook, numpy, scipy, pandas, matplotlib, seaborn, MongoDB, Elasticsearch, Kibana}
\emptySeparator
\experience
{2022}{Lead Data Scientist | Machine Learning Engineer}{WidasConcepts GmbH}{Wimsheim, Germany}
{2020} {
	\vspace{0.1cm}
	\textbf{Project}: Bosch-EBR (Experience-based Repair)
	\begin{itemize}
		\item Pioneered the development of an NLP-based vehicle identification system, employing Named Entity Recognition (NER) and Graph Theory to accurately identify and classify vehicle components.
		\item Architected and implemented a RESTful API, facilitating the efficient delivery of the vehicle identification model to stakeholders, enhancing user accessibility and system integration.
		\item Designed and developed a robust stream processing framework using Faust for EBR microservices, optimizing data handling processes and improving the system's scalability and resilience.
		\item Contributed the creation of an LLM-based Concept Identification Service, leveraging large language models to mine car part failure discussions in forums, and algorithmically identifying approved solutions to address these failures. This innovative service significantly improved the efficiency of diagnosing and resolving vehicle issues by directly linking reported problems with validated solutions.
	\end{itemize}
}
{Python, NLTK, SpaCy, Gensim, Faust, FastAPI, Elasticsearch, Kibana}
\emptySeparator
\experience
{2019}{Data Scientist}{WidasConcepts GmbH}{Wimsheim, Germany}
{2018} {
	\vspace{0.1cm}
	\textbf{Project}: Porsche-CCD (Corner Case Detection)
	\begin{itemize}
		\item Engineered a state-of-the-art spatio-temporal model that leverages internal sensory data and the geo-location of Porsche cars to detect corner cases, significantly enhancing the predictive capabilities and safety measures.
		\item Spearheaded the design and development of an interactive UI for monitoring Porsche cars, incorporating ReactJS to create a responsive and user-friendly interface that enables real-time visualization of data and identification of plausible corner cases.
		\item Developed a high-performance data streaming system utilizing MQTT and Tornado, ensuring efficient data transmission and processing capabilities for real-time monitoring and analysis.
		\item Implemented advanced data visualization techniques using Plotly and Bokeh, enabling complex data insights to be comprehensively understood through interactive graphs and charts, thus facilitating informed decision-making processes.
	\end{itemize}
}
{Python, ReactJS, Bokeh, Plotly, Tornado, MQTT, scikit-learn}
\emptySeparator
\experience
{2019}{Computer Vision Engineer | Data Scientist}{WidasConcepts GmbH}{Wimsheim, Germany}
{2018} {
	\vspace{0.1cm}
	\textbf{Project}: Chinese Painting Seal Assessment
	\begin{itemize}
		\item Pioneered the development of a cutting-edge deep learning model using state-of-the-art Convolutional Neural Networks (CNNs) in TensorFlow to accurately identify seals of Chinese artists, enabling the authentication of artworks with high precision.
		\item Innovated a recurrent neural network model designed to assess the originality of artists' seals, effectively distinguishing genuine artifacts from forgeries. This model leveraged the nuanced patterns and historical data of seal imprints, contributing significantly to the preservation of cultural heritage and the art market's integrity.

	\end{itemize}
}
{Python, Tensorflow, Keras, RNN, CNN, OpenCV, scikit-image, scikit-learn, JupyteLab, Pillow}
\emptySeparator
  \experience
  {Aug 2018}{Researcher and Developer}{DFKI GmbH}{Kaiserslautern, Germany}
  {Sep 2014} {
    \begin{itemize}
		\item Spearheaded the innovative modeling of gaze movements within the Immersive Quantified Learning lab (iQl), advancing the field of Human-Document Interaction through groundbreaking research that bridges the gap between digital learning environments and natural user engagement.
		\item Led the design and implementation of a cutting-edge Human-Computer Interaction system utilizing eye-tracking technology for the AICASys Project, markedly enhancing the accessibility of digital interfaces for individuals with disabilities, thereby democratizing technology use.
		\item Developed a novel generative probabilistic model for synthesizing eye-movement patterns, which stands as a significant contribution to understanding and predicting user interactions in digital environments, paving the way for more intuitive and adaptive systems.
		\item Contributed to academia as a Teaching Assistant for the Data Mining Course at TU Kaiserslautern, enriching the educational experience of students with practical insights and fostering a deep understanding of critical data analysis techniques.
		\item Supervised Master and Bachelor dissertations in the fields of AI and HCI at TU Kaiserslautern, guiding students through their academic journeys with mentorship that emphasizes innovation, critical thinking, and real-world application of theoretical knowledge.

    \end{itemize}
  }
    {Python, C++, R, Matlab, ZMQ, IoT, OpenCV, dlib, jupyter-notebook, numpy, scipy, pandas, matplotlib, seaborn, pillow, Edward, keras, scikit-learn, scikit-image, scikt-fuzzy, Git, TortoiseSVN}
    \emptySeparator
  \experience
  {Aug 2014}{Full-stack Developer}{Yareegar Clinic}{Tehran, Iran}
  {Nov 2013} {
    \begin{itemize}
		\item Designed a comprehensive personality assessment project for Mapna Group, successfully developing and deploying a robust evaluation system for over 20,000 employees. This initiative significantly contributed to enhancing workforce management and organizational development through tailored psychological insights.
		\item Demonstrated exceptional full-stack development skills by designing and developing a dynamic portal for psychological assessments. Utilized PHP for server-side logic and Python for data analysis and processing, showcasing a versatile proficiency in both front-end and back-end technologies. This portal facilitated seamless, efficient assessments, highlighting my ability to deliver comprehensive digital solutions from concept to deployment.

    \end{itemize}
  }
    {Python2, PHP, XAMPP, JavaScript, CSS, Autobahn|Python, TortoiseSVN, MySQL}
    \emptySeparator
  \experience
  {Nov 2013}{University Lecturer}{Azad University}{Tehran (Roudehen), Iran}
  {Sep 2012} {
    \begin{itemize}
		\item As a dedicated university lecturer, I have passionately imparted knowledge in cutting-edge subjects such as Machine Learning, Data Engineering, and Computer Vision to undergraduate Computer Science students. My approach to teaching these courses emphasizes not just the theoretical underpinnings but also practical applications, preparing students to tackle real-world challenges with innovative solutions.
		
		\item For postgraduate Clinical Psychology students, I have taught Data Analysis and Advanced Statistics, focusing on equipping them with the quantitative tools necessary to conduct rigorous research and analysis in their field. My methodology integrates statistical theories with hands-on data analysis, fostering a deep understanding of complex concepts and their application in clinical settings.

    \end{itemize}
  }
    {Python, R, SPSS, Matlab}
\end{experiences}
